---
title: "German Gredit Case"
author: "Takahiro Yamada"
date: "11/17/2021"
output: html_document
---
## Deutche Bank Credit Score Analysis
Based on Deuche Bank customer data, figuring out the scoring model using logistic regression analysis.
After confirming the regression momdels is enough reliable, created score formular.

```{r data massaging, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
##### Libraries
##############################################################
#install.packages("ggplot2")
#install.packages("plotly")
#install.packages("caret")
#install.packages("ROCR")
#install.packages("rpart") 
#install.packages("rpart.plot") 
library(ggplot2)
library(plotly)
library(caret)
library(ROCR)
library(rpart)
library(rpart.plot)


##############################################################
##### Data Massage
##############################################################
library(readxl)
my_germ <- read_excel("german credit card.xls")

any(is.na(my_germ)) 
table(my_germ$purpose) 

#omit rows with X 
which(my_germ$purpose == "X") 
my_germ[which(my_germ$purpose == "X"),] 
my_germ <- as.data.frame(my_germ)

my_germ[my_germ=="X"] <- NA
my_germ <- my_germ[-which(is.na(my_germ$purpose)),]
colSums(is.na(my_germ))

#replace good with 1, bad with 0
my_germ$binary <- gsub("good","1",my_germ$good_bad)
my_germ$binary <- gsub("bad","0",my_germ$binary) 
my_germ$binary <- as.numeric(my_germ$binary) 
```

## Data cleaing
The data sheet does not contain missing value however, contained "X" in the pourpose variable instead.
Omited the rows which contain "X" as a variables.

```{r visual analysis, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
#####Visualization
##############################################################
ggplot(data=my_germ, aes(x=marital, y=amount, color=good_bad)) +
  geom_jitter()

ggplot(data=my_germ, aes(x=depends, y=amount, color=good_bad)) +
  geom_jitter()

ggplot(data=my_germ, aes(x=duration, y=amount, color=good_bad)) +
  geom_point()+geom_smooth()+scale_color_manual(values=c("#B81CEE","#0AF0D4"))  
```

## Visual Analysis
Checked the relationship of "amount" with three variables, "marital", "depends" and "duration" using different color for good/bad customer cracification which is made by Deutche Bank.
Amount x Marital: most of customers are concentrated in status 2 and 3 / lower 5000 amount area, and good/bad looks equaly distributed.
Amount x Depends: most of customers are counted as 1.0 /lower 5000 amount area. The good/bad is equaly distributed.
Amount x Duration: good customer seems concentrated around duration 1-2 / lower 5000 amount area, and bad customer looka siaributes to the longer duration side and relatively higher amount. The smooth liner shows almost same promortion.
It is hard to figur out the significant difference between good/bad customer from these visuals.


```{r standardization normalization, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
#####Standardization, Normalization, Sampling and Classification
##############################################################
#rescale data to have a mean of 0 and a standard deviation of 1
#UDF Z-Score
standard <- function(var1) {
  my_standard <- (var1-mean(var1))/sd(var1)
  return(my_standard)
} #closing the standard variable 
#apply function to my_germ age
my_germ$age_standard <- standard(var1=my_germ$age)
mean(my_germ$age_standard)
sd(my_germ$age_standard)
summary(my_germ$age_standard)
#apply function to my_germ amount 
my_germ$amount_standard <- standard(var1=my_germ$amount)
mean(my_germ$amount_standard)
sd(my_germ$amount_standard)
summary(my_germ$amount_standard)

#UDF T-score
standard <- function(var1) {
  my_standard <- (var1-mean(var1))/sd(var1)*10+50 
  return(my_standard)
} #closing the standard variable 
#apply function to my_germ age
my_germ$age_standard <- standard(var1=my_germ$age)
mean(my_germ$age_standard)
sd(my_germ$age_standard)
summary(my_germ$age_standard)
#apply the function to my_germ amount 
my_germ$amount_standard <- standard(var1=my_germ$amount)
mean(my_germ$amount_standard)
sd(my_germ$amount_standard)
summary(my_germ$amount_standard)

###Normalization - Re-scale the values into a range of 0 and 1
normal <- function(var1){
  my_normal <- (var1-min(var1))/(max(var1)-min(var1))
  return(my_normal)
} #closing the normal UDF
my_germ$checking_norm <- normal(var1=my_germ$checking)
my_germ$duration_norm <- normal(var1=my_germ$duration)
my_germ$amount_norm <- normal(var1=my_germ$amount)
my_germ$employed_norm <- normal(var1=my_germ$employed)
my_germ$installp_norm <- normal(var1=my_germ$installp)
my_germ$age_norm <- normal(var1=my_germ$age)
my_germ$existcr_norm <- normal(var1=my_germ$existcr)
my_germ$telephon_norm <- normal(var1=my_germ$telephon)
```

## Standardization & Normalization
To see the positionnig of each customer's age and amount, created t-score UDF and created new variable age_standard and amount_standard.
Furthermore, rescale the all numeric variable range 0 to 1 for coming unitless regression calculation.


```{r logistic analysis, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
#####Classification with Logistic Regression
##############################################################
#creating training and testing data sets by random sampling
train_index <- sample(1:nrow(my_germ),size=0.8*nrow(my_germ))
germ_train <- my_germ[train_index,]
germ_test <- my_germ[-train_index,]

#linear prediction
my_linear <- lm(amount~age, data=germ_train)
summary(my_linear)

#Logistic Regression
my_logit <- glm(binary~checking + duration + age + telephon + amount + savings 
                + installp + coapp, data=germ_train, family = "binomial")
summary(my_logit)

#remove telephon and amount to improve the analysis
my_logit_better <- glm(binary~checking + duration + age + savings 
                       + installp + coapp, data=germ_train, family = "binomial")
summary(my_logit_better)

#designing logistic regression after normalization of the data
my_logit_norm <- glm(binary~checking_norm+duration_norm+age_norm+installp_norm, data=germ_train, family = "binomial")
summary(my_logit_norm)
```

## Classification with Logistic Regression
Set the "binary" converted form "good_bad" as an objective variable and other numerical variables as an explained variables tosee the which variable is significantly impacting to the good customer.Checked relationships with unit and unitless variables.
As a concequence, figure out that "chekcing", "duration", "age" and "installp", have significant relationship with good_bad variable interms of p-value.
Checking has positive stronger impact for good_bad variable.
Duration has negative stronger impact for good_bad variable.
Age has positive normal impact for good_bad variable. 
Install negative weak impact for good_bad variable.



```{r test logistic model, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
#####Confusion Matrix, Decision Tree, Type GINI and comparing different models
##############################################################
#for testing data
my_prediction_testing <- predict(my_logit,germ_test, type="response")
confusionMatrix(data=as.factor(as.numeric(my_prediction_testing > 0.5)),
                reference=as.factor(as.numeric(germ_test$binary)))

#for training data 
my_prediction_training <- predict(my_logit,germ_train, type="response")
confusionMatrix(data=as.factor(as.numeric(my_prediction_training > 0.5)),
                reference=as.factor(as.numeric(germ_train$binary)))

#AUC ROC framework
my_prediction <- my_prediction_training
pred_val_logit <- prediction(my_prediction, germ_train$binary)
perf_logit <- performance(pred_val_logit,"tpr","fpr")
plot(perf_logit)

#Challenger Decision Tree for my_Germ 
my_tree <- rpart(binary~checking_norm+duration_norm+age_norm+amount_norm+installp_norm, data=germ_train, method = "class",cp=0.02)
rpart.plot(my_tree, extra=1, type=1)
```


```{r Comparing model performance, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
#####Comparing model performance
##############################################################
my_tree_predict_testt<-predict(my_tree, germ_test,type="prob")
my_tree_predict_train<-predict(my_tree, germ_train,type="prob")
my_tree_prediction<-prediction(my_tree_predict_train[,2], germ_train$binary)

my_tree_performance<-performance(my_tree_prediction,"tpr","fpr")
plot(my_tree_performance,col="black")
plot(perf_logit,col="green3",add=TRUE)#low false positive rate more important than higher rates
```


```{r Scoring, echo=TRUE, warning=FALSE, message=FALSE}
##############################################################
#####Credit score formular 
##############################################################
#Scoring based on normarized logisitic regression
my_germ$score <- c()
for (i in 1:nrow(my_germ)) {
  my_germ$score[i] <- 20*my_germ$duration_norm[i]+
    50*my_germ$checking_norm[i]+
    40*my_germ$age_norm[i]+
    30*my_germ$installp_norm[i]
} #closing the i loop
summary(my_germ$score)

#check for both score and good_bad, if score is below score mean, label customer "outstanding"
my_germ$label <- c()

for (i in 1:nrow(my_germ)) {
  if (my_germ$score[i]<mean(my_germ$score) & my_germ$binary[i] == 1) {  
    my_germ$label[i] <- "outstanding"
  } else {
    my_germ$label[i] <- "not outstanding"
  } #closing if statement
} #closing the i loop
table(my_germ$label)
```

